Twists of supersymmetric gauge theories

### 2019-07-11 paper.tex
merge error
modest edits

\begin{dfn}
A {\bf free classical field theory} on a manifold $M$ is the data:
\begin{itemize}
\item a finite rank $\ZZ\times\ZZ/2$-graded vector bundle $E \to M$ equipped with an even differential operator of cohomological degree $+1$
\[
\d \colon \cE \to \cE [1] 
\]
such that (1) $\d^2 = 0$ and (2) $(\cE , \d)$ is an elliptic complex;
\item a map of bundles
\[
\omega\colon E \otimes E \to {\rm Dens}_M [-1]
\]
that is
\begin{enumerate}
\item fiberwise nondegenerate,
\item graded skew symmetric, and
\item satisfies $\int_M \omega\<e_0, \d e_1\> = (-1)^{|e_0|} \int_M \omega(\d e_0, e_1)$ where $e_i$ are compactly supported sections of $E$ .
\end{enumerate}
\end{itemize}
\end{dfn}

@@

\begin{dfn}
Let $(E, \d,\omega, I)$ be a classical field theory 
A {\bf strict action} of a super Lie algebra $\fg$ on $(E, \d,\omega, I)$ is a map of super dg Lie algebras
\[
\rho\colon \fg \to \left(\oloc(E)[-1] , \{-,-\}_\omega, \d + \{I,-\}_\omega\right) .
\]
More generally, an $L_\infty$ {\bf action} is an $\infty$-morphism of super dg Lie algebras
\[
\rho\colon \fg \rightsquigarrow \left(\oloc(E)[-1] , \{-,-\}_\omega, \d + \{I,-\}_\omega\right) .
\]
\end{dfn}

@@

% \cN=(8, 8) SYM
% \cN=(4, 4) SYM with matter in a pseudo-real representation
% \cN=(2, 2) SYM with matter in a complex representation

@@

>>>>

\begin{dfn}
A {\bf free classical field theory} on a manifold $M$ is the data:
\begin{itemize}
\item a finite rank $\ZZ\times\ZZ/2$-graded vector bundle $E \to M$ equipped with an even differential operator of cohomological degree $+1$
\[
\d \colon \cE \to \cE [1] 
\]
such that $(1)$: $\d^2 = 0$ and $(2)$: the pair $(\cE , \d)$ is an elliptic complex;
\item a map of bundles
\[
\omega\colon E \otimes E \to {\rm Dens}_M [-1]
\]
that is
\begin{enumerate}
\item[$(1)$] fiberwise nondegenerate,
\item[$(2)$] graded skew symmetric, and
\item[$(3)$] satisfies $\int_M \omega\<e_0, \d e_1\> = (-1)^{|e_0|} \int_M \omega(\d e_0, e_1)$ where $e_i$ are compactly supported sections of $E$ .
\end{enumerate}
\end{itemize}
\end{dfn}

@@

\begin{dfn}
Let $(E, \d,\omega, I)$ be a classical field theory 
A {\bf strict action} of a super Lie algebra $\fg$ on $(E, \d,\omega, I)$ is a map of super dg Lie algebras
\[
\rho\colon \fg \to \left(\oloc(E)[-1] , \{-,-\}_\omega, \d + \{I,-\}_\omega\right) .
\]
More generally, an $L_\infty$ {\bf action} is an $\infty$-morphism of super dg Lie algebras
\[
\rho\colon \fg \rightsquigarrow \left(\oloc(E)[-1] , \{-,-\}_\omega, \d + \{I,-\}_\omega\right) .
\]
\brian{maybe point to appendix where we can fix conventions for $\infty$-maps}
\end{dfn}

@@

% \cN=(8, 8) SYM
% \cN=(4, 4) SYM with matter in a pseudo-real representation
% \cN=(2, 2) SYM with matter in a complex representation
%BRIAN FIND REFERENCE OF BELOW
% \cN=(0,2) SYM with matter 
% \cN=(0,4) SYM with matter
% \cN=(0,8) SYM with matter

@@

\appendix

\section{Functional analysis}

\brian{We can put all our conventions for topological vector spaces, largely borrowed from \cite{CG1}, here. }

\section{$\infty$ algebra}

\brian{Not sure if this deserves a whole appendix, but it may be good to spell out what $L_\infty$ modules are, etc..}
